A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-14 6_validation.tex
moved accuracy figure down to validation section
Zjenjas analysis and some of Juns related work
lil

\paragraph{Distributed strategy}
Distribute the overfill or underfill which would happen using a naive strategy over all beads.
This maximizes robustness and minimizes narrow beads which are difficult to print.

@@

\todo{TODO: check $n$ vs $n-1$ everywhere when comparing indices and the total size! Largest index should be $n-1$, not $n$!}

@@

@@

\begin{figure}
\centering
\setlength{\figheight}{.38\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
\caption{Naive}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
\caption{Center deviation}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the naive strategy, center deivation strategy and the inward distributed strategy.
The naive method produces distinct underfill areas.
The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.
The inward distributed strategy produces the least defects.
}
\label{wedge_print}
\end{figure}

>>>>

\paragraph{Evenly distributed strategy}
Distribute the overfill or underfill which would happen using a naive strategy over all beads.
This maximizes robustness and minimizes narrow beads which are difficult to print.

@@

@@

\begin{figure}
\includegraphics[width=\columnwidth]{sources/validation/overunderfill.pdf}
\caption{total over and underfill for all data}
\label{over_underfill}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{sources/validation/smoothness.pdf}
\caption{occurrence of angles between consecutive segments}
\label{smoothness}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{sources/validation/SD.pdf}
\caption{variation in extrusion width (standard deviation)}
\label{sd}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.38\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
\caption{Naive}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
\caption{Center deviation}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the naive strategy, center deivation strategy and the inward distributed strategy.
The naive method produces distinct underfill areas.
The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.
The inward distributed strategy produces the least defects.
}
\label{prints}
\end{figure}
